The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-22 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
added sim figure

\textbf{SUSAN: SIMULATION RESULTS GO HERE}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{sim_theory_energy_jdot_Pm_1E-2_nonorm}
\caption{\edit1{Average energy (left) and angular momentum transport (right) in the total, kinetic, and magnetic components of simulation data as a function of time. Gray lines show the weakly nonlinear theory values for each quantity. }} \label{fig:sim_theory_energy_jdot}
\end{figure*}

\edit1{We analyze the average energy and angular momentum transport in the simulation domain (Figure \ref{fig:sim_theory_energy_jdot}).  }

%\textbf{SUSAN: SIMULATION RESULTS GO HERE}
